Sex and Power: Sexual dimorphism in trait variability and its eco-evolutionary

### 2020-05-19 scripts/MouseSexDiffApril20_2020.Rmd
Small fixes for renderinga nd trying abunch of stuff tos ee ifw e can sort PDF, no luck

---
title: 'Sex and Power: Sexual dimorphism in trait variability and its eco-evolutionary
  and statistical implications'
author: Susanne Zajitschek,  Felix Zajitschek, Russell Bonduriansky, Robert  Brooks,
  Will Cornwell, Daniel Falster, Malgorzata Lagisz, Jeremy Mason, Alistair Senior,
  Daniel Noble, & Shinichi Nakagawa
date: "`r Sys.Date()`"
output:
  bookdown::html_document2:
    code_folding: hide
    number_sections: yes
    theme: flatly
    toc: yes
    toc_depth: 6
    toc_float: yes
  word_document:
    toc: yes
    toc_depth: '4'
  html_notebook:
    toc: yes
  pdf_document:
    toc: yes
    toc_depth: '4'
  html_document:
    df_print: paged
    toc: yes
    toc_depth: '4'
subtitle: Electronic Supplementary Material
always_allow_html: yes
---

@@

```{r, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  cache = TRUE,
  tidy = TRUE
)
```

@@

# Meta-analysis results
## Preparing: Figure 3 
### Count data, based on First-order meta-analysis results
This includes all separate eligible traits.
Re-ordering of grouping terms. 
Preparation of subplot 4A

@@

## Figure
Figure \@ref(fig:FigS1) is similar to Figure 3 in the main article except that lnVR has been added to the plot for comparison with lnCVR and lnRR.

## Figure

# Supplemental Tables
## Table

@@

@@

   pander(ST1, caption = "Table 6.1: Summary of the available numbers of male and female mice from each strain and originating institution.")

    #kable(ST1, caption = "Summary of the available numbers of male and female mice from each strain and originating institution.") %>%
    #kable_styling() %>%
    #pander()
    #scroll_box(width = "100%", height = "200px")

@@

## Table

@@

pander(cbind(meta1 %>% count(parameter_group)), caption = "Table 6.2: Trait categories (parameter_group) and the number of correlated traits within these categories. Traits were meta-analysed using robumeta")

@@

## Table

@@

pander(metacombo, caption = "Table 6.3: We use this corrected (for correlated traits) results table, which contains each of the meta-analytic means for all effect sizes of interest, for further analyses.  We further use this table as part of the Shiny App, which is able to provide the percentage differences between males and females for mean, variance and coefficient of variance.")

#kable(metacombo, digits = 3, caption = "We use this corrected (for correlated traits) results table, which contains each of the meta-analytic means for all effect sizes of interest, for further analyses.  We further use this table as part of the Shiny App, which is able to provide the percentage differences between males and females for mean, variance and coefficient of variance.") %>%
  #kable_styling() %>%
  #scroll_box(width = "100%", height = "200px")

@@

## Table

@@

pander(overall2, caption = "Table 6.4: Summary of overall meta-analyses on the functional trait group level (GroupingTerm). Results for lnCVR, lnVR and lnRR and their respective upper and lower 95 percent CI's, standard error and I2 values are provided.")

#kable(overall2, digits = 3, caption = "Summary of overall meta-analyses on the functional trait group level (GroupingTerm). Results for lnCVR, lnVR and lnRR and their respective upper and lower 95 percent CI's, standard error and I2 values are provided.") %>%
 #  kable_styling() %>%
#  scroll_box(width = "100%", height = "200px")
```

## Table

@@

    pander(mf_sig, caption = "Table 6.5: Provides an overview of meta-analysis results performed on traits that were significantly biased towards either sex. This table summarizes findings for both sexes and the respective functional trait groups.")

  #kable(mf_sig, digits = 3, caption = "Provides an overview of meta-analysis results performed on traits that were significantly biased towards either sex. This table summarizes findings for both sexes and the respective functional trait groups.") %>%
   # kable_styling() %>%
  # scroll_box(width = "100%", height = "300px")
```

## Table

@@

  pander(het, caption = "Table 6.6: Summarizes our findings on heterogeneity due to institutions and mouse strains. These results are based on meta-analyses on sigma^2 and errors for mouse strains and centers (Institutions), following the identical workflow from above.")

  #kable(het, digits = 3, caption = "Summarizes our findings on heterogeneity due to institutions and mouse strains. These results are based on meta-analyses on sigma^2 and errors for mouse strains and centers (Institutions), following the identical workflow from above.") %>%
   # kable_styling() %>%
    #scroll_box(width = "100%", height = "200px")

>>>>

---
title: 'Sex and Power: Sexual dimorphism in trait variability and its eco-evolutionary
  and statistical implications'
author: Susanne Zajitschek,  Felix Zajitschek, Russell Bonduriansky, Robert  Brooks,
  Will Cornwell, Daniel Falster, Malgorzata Lagisz, Jeremy Mason, Alistair Senior,
  Daniel Noble, & Shinichi Nakagawa
date: "`r Sys.Date()`"
output:
  bookdown::pdf_document2:
    toc: yes
    toc_depth: 6
    number_sections: true
    theme: flatly
  word_document:
    toc: yes
    toc_depth: '4'
  html_notebook:
    toc: yes
  bookdown::html_document2:
    code_folding: hide
    number_sections: yes
    theme: flatly
    toc: yes
    toc_depth: 6
    toc_float: yes
  html_document:
    df_print: paged
    toc: yes
    toc_depth: '4'
subtitle: Electronic Supplementary Material
always_allow_html: yes
---

@@

```{r, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  cache = TRUE,
  tidy = TRUE,
  tidy.opts=list(width.cutoff=80)
)
```

@@

# Meta-analysis results
## Preparing: Figure 3 
### Count data, based on First-order meta-analysis results
This includes all separate eligible traits.
Re-ordering of grouping terms. Preparation of subplot 3A

@@

@@

## Figure 5.1
Figure \@ref(fig:FigS1) is similar to Figure 3 in the main article except that lnVR has been added to the plot for comparison with lnCVR and lnRR.

## Figure 5.2

# Supplemental Tables
## Table 6.1

@@

  #PDF
 pander(ST1, caption = "Table 6.1: Summary of the available numbers of male and female mice from each strain and originating institution.")
  #HTML
    #kable(ST1, caption = "Summary of the available numbers of male and female mice from each strain and originating institution.") %>%
    #kable_styling() %>%
    #scroll_box(width = "100%", height = "200px")

@@

## Table 6.2

@@

#PDF
pander(cbind(meta1 %>% count(parameter_group)), caption = "Table 6.2: Trait categories (parameter_group) and the number of correlated traits within these categories. Traits were meta-analysed using robumeta")

@@

## Table 6.3

@@

# PDF
pander(metacombo, caption = "Table 6.3: We use this corrected (for correlated traits) results table, which contains each of the meta-analytic means for all effect sizes of interest, for further analyses.  We further use this table as part of the Shiny App, which is able to provide the percentage differences between males and females for mean, variance and coefficient of variance.")

#HTML
#kable(metacombo, digits = 3, caption = "We use this corrected (for correlated traits) results table, which contains each of the meta-analytic means for all effect sizes of interest, for further analyses.  We further use this table as part of the Shiny App, which is able to provide the percentage differences between males and females for mean, variance and coefficient of variance.") %>%
  #kable_styling() %>%
  #scroll_box(width = "100%", height = "200px")

@@

## Table 6.4

@@

#PDF
pander(overall2, caption = "Table 6.4: Summary of overall meta-analyses on the functional trait group level (GroupingTerm). Results for lnCVR, lnVR and lnRR and their respective upper and lower 95 percent CI's, standard error and I2 values are provided.")

#HTML
#kable(overall2, digits = 3, caption = "Summary of overall meta-analyses on the functional trait group level (GroupingTerm). Results for lnCVR, lnVR and lnRR and their respective upper and lower 95 percent CI's, standard error and I2 values are provided.") %>%
#kable_styling() %>%
#scroll_box(width = "100%", height = "200px")
```

## Table 6.5

@@

        #PDF
    pander(mf_sig, caption = "Table 6.5: Provides an overview of meta-analysis results performed on traits that were significantly biased towards either sex. This table summarizes findings for both sexes and the respective functional trait groups.")  
      #HTML
  #kable(mf_sig, digits = 3, caption = "Provides an overview of meta-analysis results performed on traits that were significantly biased towards either sex. This table summarizes findings for both sexes and the respective functional trait groups.") %>%
  #kable_styling() %>%
  #scroll_box(width = "100%", height = "300px")
```

## Table 6.6

@@

  # PDF
  pander(het, caption = "Table 6.6: Summarizes our findings on heterogeneity due to institutions and mouse strains. These results are based on meta-analyses on sigma^2 and errors for mouse strains and centers (Institutions), following the identical workflow from above.")

  # HTML
  #kable(het, digits = 3, caption = "Summarizes our findings on heterogeneity due to institutions and mouse strains. These results are based on meta-analyses on sigma^2 and errors for mouse strains and centers (Institutions), following the identical workflow from above.") %>%
   #kable_styling() %>%
    #scroll_box(width = "100%", height = "200px")
